\documentclass[../notes.tex]{subfiles}

\pagestyle{main}
\renewcommand{\chaptermark}[1]{\markboth{\chaptername\ \thechapter\ (#1)}{}}
\setcounter{chapter}{4}

\begin{document}




\chapter{Consequences of Defining Infinity}
\section{Office Hours}
\begin{itemize}
    \item \marginnote{4/15:}There will not be anything explicit about Thursday's content, but knowing it is helpful for understanding conformal maps.
    \item The exam is completely closed book.
    \item Midterm-style questions.
    \begin{itemize}
        \item Per the mathematical hierarchy of needs (definitions and examples, theorem statements, problems/applying them, proofs of them).
        \item He does not want to test our memorization skills but rather our understanding.
    \end{itemize}
\end{itemize}



\section{Midterm Review Sheet}
\begin{itemize}
    \item \marginnote{4/16:}Properties of complex numbers.
    \item \textbf{Holomorphic} ($f$ at $z_0$): A function $f:\C\to\C$ for which the following limit exists. \emph{Also known as} \textbf{$\pmb{\C}$-differentiable}. \emph{Constraints}
    \begin{equation*}
        \lim_{z\to z_0}\frac{f(z)-f(z_0)}{z-z_0} =: f'(z_0)
        \qquad\Longleftrightarrow\qquad
        f(z) = f(z_0)+\Delta(z)(z-z_0)
    \end{equation*}
    where $\Delta$ is continuous at $z_0$ and $\Delta(z_0)=f'(z_0)$.
    \begin{itemize}
        \item Sum rule, product rule, quotient rule.
        \item Chain rule.
        \item Holomorphic implies continuous.
    \end{itemize}
    \item Every $\C$-linear map is just multiplication by a complex number; the matrix must compute with $\mathcal{M}(i)$.
    \item \textbf{Cauchy-Riemann equations}: The following two equations, which identify when a complex function $(x,y)\mapsto(g,h)$ is holomorphic. \emph{Also known as} \textbf{CR equations}. \emph{Given by}
    \begin{align*}
        g_x &= h_y\\
        g_y &= -h_x
    \end{align*}
    \item \textbf{Wirtinger derivatives}: The two differential operators defined as follows. \emph{Denoted by} $\bm{\partial/\partial z,\partial/\partial\bar{z}}$. \emph{Given by}
    \begin{align*}
        \pdv{\bar{z}} &:= \frac{1}{2}\left( \pdv{x}+i\pdv{y} \right)&
        \pdv{z} &:= \frac{1}{2}\left( \pdv{x}-i\pdv{y} \right)
    \end{align*}
    \item Theorem: The $\R$-differentiable function $f:U\to\C$ is holomorphic iff $\pdv*{f}{\bar{z}}=0$. Moreover, if it is, then
    \begin{equation*}
        f'(z_0) = \eval{\pdv{f}{z}}_{z_0}
    \end{equation*}
    \item \textbf{Laplacian}: The differential operator defined as follows. \emph{Denoted by} $\bm{\Delta}$. \emph{Given by}
    \begin{equation*}
        \Delta := \pdv[2]{x}+\pdv[2]{y}
    \end{equation*}
    \item \textbf{Harmonic} (function): A function $f:\R^2\to\C$ such that $\Delta f=0$.
    \item Corollary: The real and imaginary parts of a $C^2$ holomorphic function are harmonic.
    \begin{proof}
        $\Delta(u+iv)=\Delta u+i\Delta v$.
    \end{proof}
    \item \textbf{Harmonic conjugates}: Two functions $u,v:\R^2\to\R$ that satisfy the CR equations.
    \item Path integration:
    \begin{equation*}
        \int_\gamma f\dd{z} = \int_a^bf(\gamma(t))\cdot\gamma'(t)\dd{t}
    \end{equation*}
    \item FTC: Suppose $F'=f$ on $U\subset\C$, and let $\gamma$ be a \textbf{path} inside of $U$. Then
    \begin{equation*}
        \int_\gamma f\dd{z} = F(\gamma(b))-F(\gamma(a))
    \end{equation*}
    \item Factoring into rotation and scaling matrices.
    \begin{equation*}
        \begin{pmatrix}
            a & -b\\
            b & a\\
        \end{pmatrix}
        =
        \begin{pmatrix}
            \cos\theta & -\sin\theta\\
            \sin\theta & \cos\theta\\
        \end{pmatrix}
        \begin{pmatrix}
            \lambda & 0\\
            0 & \lambda\\
        \end{pmatrix}
        \tag{$\lambda,\theta\in\R$}
    \end{equation*}
    \item Lemma: Holomorphic maps preserve angles.
    \begin{proof}
        Look at the argument at the intersection point and use the chain rule.
    \end{proof}
    \item \textbf{Conformal} (map): A function $f:U\to V$, where $U,V\subset\C$, that satisfies the following two constraints. \emph{Constraints}
    \begin{enumerate}
        \item $f$ is a diffeomorphism.
        \item $f$ preserves angles.
    \end{enumerate}
    \item \textbf{Diffeomorphism}: A homeomorphism for which $f,f^{-1}$ are differentiable.
    \item \textbf{Biholomorphic} (map): A function $f:U\to V$ that is bijective, holomorphic, and for which $f^{-1}$ is holomorphic.
    \item Theorem/observation: Biholomorphic iff conformal.
    \item Chain rule:
    \begin{equation*}
        \pdv{t}(f\circ g)(z) = f_z(g(z))g_z(z)+f_{\bar{z}}(g(z))\bar{g}_{\bar{z}}(z)
    \end{equation*}
    \item \textbf{Complex linear map}: A map $l:\C\to\C$ characterized by the following. \emph{Constraints}
    \begin{enumerate}
        \item $l(z+w)=l(z)+l(w)$;
        \item $l(rz)=rl(z)$;
    \end{enumerate}
    for $z,w,r\in\C$.
    \begin{itemize}
        \item Every complex linear map is of the form
        \begin{equation*}
            w = l(z) = az
        \end{equation*}
        for a unique $a\in\C$.
    \end{itemize}
    \item \textbf{Real linear map}: A map $l:\C\to\C$ characterized by the following. \emph{Constraints}
    \begin{enumerate}
        \item $l(z+w)=l(z)+l(w)$;
        \item $l(rz)=rl(z)$;
    \end{enumerate}
    for $z,w\in\C$ and $r\in\R$.
    \begin{itemize}
        \item Every real linear map is of the form
        \begin{equation*}
            w = l(z)
            = az+b\bar{z}
            =
            \begin{pmatrix}
                a & b\\
            \end{pmatrix}
            \begin{pmatrix}
                z\\
                \bar{z}\\
            \end{pmatrix}
        \end{equation*}
        for a unique pair $
            \begin{pmatrix}
                a & b\\
            \end{pmatrix}
            \in\C^2
        $.
        \item Implication: $l$ is complex linear iff $b=0$.
    \end{itemize}
    \item \textbf{Tangent map} (of $f$ at $z_0$): The real linear map from $\C\to\C$ determined by the vector $
        \begin{pmatrix}
            f_z(z_0) & f_{\bar{z}}(z_0)\\
        \end{pmatrix}
    $.
    \item Proposition: $f$ is holomorphic at $z_0$ iff its tangent map at $z_0$ is complex linear.
    \item \textbf{Exponential function}: The complex function defined as follows. \emph{Denoted by} $\textbf{e}^{\bm{z}}$, $\textbf{exp}\bm{(z)}$. \emph{Given by}
    \begin{equation*}
        \e[z] = \exp(z) := \sum_{k=0}^\infty\frac{z^k}{k!}
    \end{equation*}
    \item \textbf{Pointwise} (convergent $\{f_n\}$): A sequence of functions $f_n:\C\to\C$ such that for all $z\in\C$, we have $f_n(z)\to f(z)$.
    \item \textbf{Locally uniformly} (convergent $\{f_n\}$): A sequence of functions $f_n:U\to\C$ and a function $f:U\to\C$ such that for all compact $K\subset U$,
    \begin{equation*}
        \sup_{z\in K}|f_n(z)-f(z)| \to 0
    \end{equation*}
    \item Lemma: If $f_n\to f$ locally uniformly and the $f_n$ are continuous (or integrable; \emph{not} differentiable), then so is $f$.
    \item \textbf{Taylor's theorem}: If $f:\R\to\R$ is $C^{k+1}$ and $P_\alpha^k(x)$ is the $k^\text{th}$ Taylor polynomial about $\alpha\in\R$, then for all $\beta\in\R$, there exists some $x\in(\alpha,\beta)$ such that
    \begin{equation*}
        f(\beta)-P_\alpha^k(\beta) = \frac{(\beta-\alpha)^{k+1}}{(k+1)!}f^{(k+1)}(x)
    \end{equation*}
    \item \textbf{Analytic} (function): A function $f:\R\to\R$ for which the Taylor polynomials converge (locally uniformly) to $f$.
    \item \textbf{Absolutely} (locally uniformly convergent power series): A power series $P(z)=\sum_{k=0}^\infty a_kz^k$ for which $A_N:\C\to\R$ locally uniformly converges, where
    \begin{equation*}
        A_N(z) := \sum_{k=0}^N|a_kz^k|
    \end{equation*}
    \item \textbf{Geometric series test}: If $|z|<1$, then
    \begin{equation*}
        \sum_{k=0}^\infty z^k \to \frac{1}{1-z}
    \end{equation*}
    \item Lemma: Let $P(z)$ be a power series about 0. If there exists $z_1\neq 0$ such that $|a_kz_1^k|\leq M$ for all $k$, then $P(z)=\sum a_kz^k$ converges on the disk $|z|<|z_1|$.
    \begin{proof}
        Choice of $z_1,z_2$, and their ratio.
    \end{proof}
    \item \textbf{Disk of convergence}: The largest disk centered at zero on which you converge.
    \item \textbf{Radius of convergence}: The radius of the disk of convergence. \emph{Denoted by} $\bm{r}$.
    \item \textbf{Cauchy-Hadamard formula}: The radius of convergence is given by
    \begin{equation*}
        r = (\limsup|a_k|^{1/k})^{-1}
    \end{equation*}
    \item Lemma (from real analysis): If $f_n\to f$ locally uniformly and $f_n'\to g$ locally uniformly, then $f$ is differentiable and $f'=g$.
    \begin{itemize}
        \item Implication: Convergent power series are holomorphic.
    \end{itemize}
    \item Corollary: Power series representations are unique.
    \begin{enumerate}
        \item If $P(z)=\sum a_kz^k$ is convergent, then
        \begin{equation*}
            a_k = \frac{1}{k!}P^{(k)}(0)
        \end{equation*}
        \item If $P(z)=0$ in a neighborhood of zero, then $a_k=0$ for all $k$.
        \item If $P(z)=Q(z)$ (where $Q(z)=\sum b_kz^k$) in a neighborhood of 0, then $a_k=b_k$ for all $k$.
    \end{enumerate}
    \item Properties of the complex exponential.
    \begin{enumerate}
        \item $\exp(z)=[\exp(z)]'$.
        \begin{itemize}
            \item We obtain this via term-by-term differentiability.
            \item This is just our favorite formula $\dv*{t}(\e[t])=\e[t]$ from calculus.
        \end{itemize}
        \item $\overline{\exp(z)}=\exp(\bar{z})$.
        \item $\exp(a+b)=\exp(a)\cdot\exp(b)$.
        \item $|\exp(z)|=\exp[\re(z)]$.
        \item $\e[iz] = \cos(z)+i\sin(z)$.
    \end{enumerate}
    \item Complex trigonometric functions.
    \begin{align*}
        \cos(z) &:= \frac{1}{2}(\e[iz]+\e[-iz])&
        \sin(z) &:= \frac{1}{2i}(\e[iz]-\e[-iz])\\
        \cosh(z) &:= \cos(iz)&
        \sinh(z) &:= i\sin(iz)
    \end{align*}
    \item \textbf{Domain}: A connected, open set $U\subset\C$.
    \item \textbf{Primitive} (of $f$): A differentiable function whose derivative is equal to the original function $f$. \emph{Also known as} \textbf{antiderivative}, \textbf{indefinite integral}. \emph{Denoted by} $\bm{F}$.
    \item Corollary to the FTC: If $f=F'$, then for any closed curve $\gamma$ in $U$,
    \begin{equation*}
        \int_\gamma f\dd{z} = 0
    \end{equation*}
    \item Proposition: If $f:U\to\C$ is continuous and $\int_\gamma f\dd{z}=0$ for every closed loop in $U$, then $f$ has a primitive on $U$.
    \begin{proof}
        Step 1: Choose the integral along arbitrary $\gamma$.\par
        Step 2: Choice of $\gamma$ doesn't matter (closed loop condition).\par
        Step 3: Correct derivative; apply FTC along $\delta$ and take limit.
    \end{proof}
    \item \textbf{Star-shaped} (domain): A domain $U\subset\C$ for which there exists $a\in U$ such that for all $z\in U$, the segment $a\to z$ is in $U$.
    \item Lemma: If $U$ is star-shaped and for every triangle with one vertex at $a$, we have $\int_\triangle f\dd{z}=0$, then $f$ has a primitive in $U$.
    \item \textbf{Cauchy Integral Theorem}: Suppose $U$ is a star-shaped domain and $f:U\to\C$ is holomorphic. Then $\int_\gamma f\dd{z}=0$ for any closed loop $\gamma$ in $U$.
    \begin{proof}
        Step 1: Prove $f$ has a primitive via lemma \& Goursat's lemma.\par
        Step 2: Apply FTC.
    \end{proof}
    \item \textbf{Goursat's lemma}: If $f$ is holomorphic in a neighborhood of a triangle including the interior, then $\int_\triangle f\dd{z}=0$.
    \begin{proof}
        Subdividing triangles and inequalities.
    \end{proof}
    \item Evaluating integrals using the complex functions and various paths.
    \item \textbf{Ratio test}: For $\sum a_n$, think about
    \begin{equation*}
        \lim_{n\to\infty}\left| \frac{a_{n+1}}{a_n} \right|
    \end{equation*}
    \item \textbf{Root test}: For $\sum a_n$, think about
    \begin{equation*}
        \lim_{n\to\infty}\left| a_n \right|^{1/n}
    \end{equation*}
    \item \textbf{Majorant test}: If $\sum_{k=0}^\infty a_k$ is a convergent series with positive terms and if for almost all $k$ and all $z\in M$ we have $|f_k(z)|\leq a_k$, then $\sum_{k=0}^\infty f_k$ is absolutely uniformly convergent on $M$.
    \item Exponential mappings.
    \begin{itemize}
        \item $z=x+iy_0$ maps onto the open ray beginning at 0 and passing through $\e[iy_0]$.
        \item $z=x_0+iy$ maps onto the circle of radius $\e[x_0]$.
        \item Half-open horizontal strips map bijectively onto $\C^*$.
    \end{itemize}
    \item \textbf{Homotopic} (paths): Two paths $\gamma,\tilde{\gamma}\subset U$ a domain such that $\tilde{\gamma}$ is obtained from $\gamma$ by modifying $\gamma$ on a small disk $D\subset U$, keeping the endpoints fixed.
    \item Claim/TPS: This argument shows that if $\gamma$ and $\tilde{\gamma}$ are homotopic in $U$ and $f\in\mO(U)$, then
    \begin{equation*}
        \int_\gamma f\dd{z} = \int_{\tilde{\gamma}}f\dd{z}
    \end{equation*}
    \begin{proof}
        Each bump is a closed loop for the CIT.
    \end{proof}
    \item Corollary: Let $U$ be any domain, $D$ be a disk in $U$, and $z\in\mathring{D}$. Suppose $f\in\mO(U\setminus\{z\})$ and is bounded near $z$. Then
    \begin{equation*}
        \int_{\partial D}f\dd{z} = 0
    \end{equation*}
    \begin{proof}
        Homotopy and $\gamma_\varepsilon$.
    \end{proof}
    \item \textbf{Cauchy Integral Formula}: Suppose $U$ is any domain, $D\subset U$ is a disk (i.e., $D\subset\subset U$ or $\overline{D}\subset U$), $f\in\mO(U)$, and $z\in D$. Then
    \begin{equation*}
        f(z) = \frac{1}{2\pi i}\int_{\partial D}\frac{f(\zeta)}{\zeta-z}\dd\zeta
    \end{equation*}
    \begin{proof}
        Define the helper function
        \begin{equation*}
            g(\zeta) =
            \begin{cases}
                \frac{f(\zeta)-f(z)}{\zeta-z} & \zeta\neq z\\
                f'(z) & \zeta=z
            \end{cases}
        \end{equation*}
        It integrates to zero on $\partial D$ and then splits into the two sides of the CIF.
    \end{proof}
    \item Corollary: Holomorphic functions are $C^\infty$.
    \item Corollary: In general,
    \begin{equation*}
        f^{(n)}(z) = \frac{n!}{2\pi i}\int_{\partial D}\frac{f(\zeta)}{(\zeta-z)^{n+1}}\dd\zeta
    \end{equation*}
    \item \textbf{Cauchy's inequalities}:
    \begin{equation*}
        |f^{(n)}(z)| \leq \frac{n!}{R^n}\max_{\partial D}|f(\zeta)|
    \end{equation*}
    \item Liouville's Theorem: Suppose $f\in\mO(\C)$ (i.e., $f$ is \textbf{entire}) and $f$ is bounded. Then it's constant.
    \begin{proof}
        Cauchy's inequalities on a really big disk to limit $|f'|$.
    \end{proof}
    \item \textbf{Entire} (function): A complex-valued function that is holomorphic on the whole complex plane.
    \item The Identity Theorem: If two holomorphic functions $f,g\in\mO(U)$ agree on an open set in $U$, then $f=g$.
    \begin{proof}
        True for power series.
    \end{proof}
    \begin{itemize}
        \item In fact, more is true: If $z_n\to z_0$ where each $z_n$ is distinct and $f(z_n)=g(z_n)$ for all $n$, then $f=g$.
    \end{itemize}
    \item \textbf{Analytic continuation} (of $f$): The function $g\in\mO(V)$ where $f\in\mO(U)$, $V\supset U$, and $f=g$ on $U$.
    \item Morera's Theorem: If $U$ is any domain, $f:U\to\C$ is continuous, and $\int_\triangle f\dd{z}=0$ for all triangles, then $f$ is holomorphic.
    \begin{proof}
        The primitive exists. The primitive is holomorphic. Therefore, $F'=f$ is holomorphic.
    \end{proof}
    \item \textbf{Riemann's removable singularity theorem}: Suppose $U$ is a domain, $z\in U$, $f\in\mO(U\setminus\{z\})$, and $f$ is bounded near $z$. Then there exists a unique analytic continuation $\hat{f}\in\mO(U)$. \emph{Also known as} \textbf{Riemann extension theorem}.
    \begin{proof}
        Define a helper function
        \begin{equation*}
            F(\zeta) =
            \begin{cases}
                f(\zeta)(\zeta-z) & \zeta\neq z\\
                0 & \zeta=z
            \end{cases}
        \end{equation*}
        Use Morera's theorem: $F$ is continuous, triangles in two cases (CIT and $\gamma_\varepsilon$), and $F'=f$ via the limit definition.
    \end{proof}
    \item \textbf{Singularity} (of $f$): A point $z_0$ such that $f\in\mO(U\setminus\{z_0\})$.
    \item \textbf{Removable} (singularity): A singularity of a function that that satisfies the hypotheses of Riemann's removable singularity theorem.
    \item If a singularity is not removable, then $f$ is not bounded near $z_0$. This leads to additional definitions.
    \item \textbf{Pole}: A non-removable singularity $z_0$ of a function $f$ for which $|f(z)|\to\infty$ as $z\to z_0$.
    \begin{itemize}
        \item So-named because of real analysis where a pole is an asymptote, and asymptotes kind of look like poles!
    \end{itemize}
    \item \textbf{Essential} (singularity): A non-removable singularity that is not a pole; equivalently, a singularity $z_0$ for which there exist sequences $z_n\to z_0$ and $w_n\to z_0$ such that $|f(z_n)|\to\infty$ and $|f(w_n)|$ stays bounded.
    \item \textbf{Meromorphic} (function): A function $f:U\to\C$ such that $f\in\mO(U\setminus P)$ and each $p\in P$ is a pole, where $P\subset U$ is a finite set of points.
    \item Orders of zeros and poles.
    \begin{itemize}
        \item Invert the function, find a power series, divide $(z-p)^L$ out, find the power series of $h$, invert, find the principal part of the \textbf{Laurent series}.
    \end{itemize}
    \item Theorem (maximum modulus principle): Let $f\in\mO(U)$. If $|f(z)|$ has a local maximum on $U$, then $f$ is constant.
    \begin{proof}
        Step 1: Long inequality through the CIF that becomes equality.\par
        Step 2: Subtract and get integrand equal to zero; $|f|$ is constant on $\partial D$.\par
        Step 3: $|f|^2$ is constant on $\partial D$, differentiate, casework to $f$ is constant or zero.
    \end{proof}
    \item Corollary (minimum modulus principle): If $f\in\mO(U)$, $f\neq 0$ on $U$ (hence $1/f\in\mO(U)$), and $|f(z)|$ takes a minimum in $U$, then $f$ is constant.
\end{itemize}



\section{Midterm}
\subsection*{T/F: 5 points each (1 for answer, 4 for explanation)}
Indicate whether each of the following are true or false, and give a complete answer as to why.
\begin{enumerate}
    \item Any entire function (i.e., any $f\in\mO(\C)$) is the derivative of another entire function.
    \item Let $U$ be a domain, let $z$ be a point in $U$, and let $f\in\mO(U\setminus\{z\})$. Suppose that $\int_\gamma f\dd{z}=0$ for every closed curve $\gamma$ in $U\setminus\{z\}$. Then $f\in\mO(U)$.
    \item If $f,g\in\mO(\C)$ and there are two distinct points $z_1,z_2\in\C$ such that
    \begin{equation*}
        f(z_1)-g(z_1) \neq f(z_2)-g(z_2)
    \end{equation*}
    then there is a sequence of points $z_n\in\C$ such that $|f(z_n)-g(z_n)|\to\infty$.
    \item For any sequence of positive real numbers $\{a_k\}$ and any point $z\in\C$, there is a function $f$, holomorphic in a neighborhood of $z$, such that $|f^{(k)}(z)|=a_k$.
    \item There is a conformal map that does all of the following.
    \begin{itemize}
        \item Takes the first quadrant $Q=\{z:\re(z),\im(z)>0\}$ to the strip $S=\{z:\im(z)\in(-2,2)\}$.
        \item Takes the ray $\{z\in Q:\re=\im(z)\}$ to the "sine graph," i.e., $\{z:\im(z)=\sin[\re(z)]\}$.
        \item Takes the segment $\{z\in Q:\re(z)+\im(z)=1\}$ to $S\cap i\R$.
    \end{itemize}
\end{enumerate}


\subsection*{Problems: 5 points each}
In the following, please \emph{fully explain your reasoning} in addition to doing any relevant computations. A correct answer without explanation will receive at most one point on the problem.
\begin{enumerate}[label={\textbf{\arabic*.}}]
    \item Show that $u(x+iy)=\e[2x]\sin(2y)+2x$ is harmonic on $\C$ and find a harmonic conjugate. \emph{Bonus (1pt)}: If $v$ is your harmonic conjugate, express the holomorphic function $f=u+iv$ in terms of $z$.
    \item Suppose that $U$ is a domain, $P$ is a countable set of points in $U$, and that $f\in\mO(U\setminus P)$. Suppose further that $f$ has a pole at each point of $P$. Prove that $P$ is discrete in $U$ (i.e., $P$ does not have any accumulation points in $U$).
    \item Suppose I tell you that $f(z)=1/(z-a)$, but I don't tell you what $a$ is. Suppose that you know the real and imaginary parts of $a$ are irrational and that you have an oracle that can compute $\int_\gamma f\dd{z}$ over any path such that the real and imaginary parts of $\gamma(t)$ are always rational (i.e., any $\gamma$ that lives in $\Q+i\Q$). How would you go about estimating the value of $a$?
    \item 
    \begin{enumerate}
        \item Show that if $\{a_k\}$ is a sequence of non-zero complex numbers, then
        \begin{equation*}
            \lim_{k\to\infty}\frac{|a_k|}{|a_{k-1}|} = L
            \qquad\Longrightarrow\qquad
            \lim_{k\to\infty}|a_k|^{1/k} = L
        \end{equation*}
        \item Find the radius of convergence of the \textbf{order 0 Bessel function}
        \begin{equation*}
            J_0(z) = \sum_{n=0}^\infty\frac{(-1)^n}{2^{2n}(n!)^2}z^{2n}
        \end{equation*}
    \end{enumerate}
    \item Suppose that $f$ is a function on $\C$ such that\dots
    \begin{enumerate}
        \item $f$ is ($+i$) anti-periodic, that is, if $f$ is defined at $z$ then it is defined at $z+i$ and $f(z)=-f(z+i)$;
        \item $f$ is holomorphic in the strip $\{z\mid\im(z)\in(-0.1,1.1)\}$ except at the point $z=i/2$;
        \item If $\gamma$ denotes a \emph{clockwise} circle of radius $1/2$ centered at $i/2$, then $\int_\gamma f\dd{z}=17$;
        \item $|f(z)|\to 0$ as $\re(z)\to\pm\infty$.
    \end{enumerate}
    Compute $\int_{-\infty}^\infty f(x)\dd{x}$.
\end{enumerate}



\section{The Riemann Sphere}
\begin{itemize}
    \item \marginnote{4/18:}Midterms are 2/3 graded.
    \item Project proposal due on Monday by the end of the day.
    \begin{itemize}
        \item Completion points; Calderon just wants to give us feedback.
    \end{itemize}
    \item PSets 4 and 5 will be pushed back by 1 week.
    \begin{itemize}
        \item Get started on your final project in the intervening time!
    \end{itemize}
    \item Today.
    \begin{itemize}
        \item More holomorphic and meromorphic functions.
        \item Definition of the logarithm.
    \end{itemize}
    \item Example: Consider
    \begin{equation*}
        f(z) = \frac{1}{z}
        \in \mO(\C^*)
    \end{equation*}
    How does this look as a conformal map, e.g., where does it send the following two sets?
    \begin{align*}
        \D\setminus\{0\}&&
        \{r\e[i\theta]\mid\theta\text{ fixed}\}
    \end{align*}
    \begin{itemize}
        \item $\D\setminus\{0\}$ goes to $\C\setminus\overline{\D}$.
        \item $\{r\e[i\theta]\mid\theta\text{ fixed}\}$ goes to the line opposite itself at $\theta+\ang{180}$.
        \begin{itemize}
            \item This is because $1/z$ takes $r\e[i\theta]$ to $r^{-1}\e[-i\theta]$.
            \item Moreover, as $r\to\infty$ in the initial set, $r^{-1}\to 0$ in the image.
        \end{itemize}
        \item Observe that
        \begin{align*}
            \lim_{z\to 0}|f(z)| &= \infty&
            \lim_{|z|\to\infty}f(z) &= 0
        \end{align*}
        \item So can't we just say that $f(0)=\infty$ and $f(\infty)=0$?
        \begin{itemize}
            \item Sure! Add in $\infty$ like with the extended real numbers.
            \item We just stated that we can define $i:=\sqrt{-1}$ to be a thing, so why not $\infty$ as well?
        \end{itemize}
        \item We now make this definition a bit more rigorous.
    \end{itemize}
    \item \textbf{Riemann sphere}: The $S^2$-like manifold defined as follows. \emph{Denoted by} $\bm{\hat{\pmb{\C}}}$. \emph{Given by}
    \begin{equation*}
        \hat{\C} := \C\cup\{\infty\}
    \end{equation*}
    \begin{itemize}
        \item We can thus define a \textbf{neighborhood} (of $\infty$).
    \end{itemize}
    \item \textbf{Neighborhood} (of $\infty$): The set defined as follows. \emph{Given by}
    \begin{equation*}
        \{|z|>R\}\cup\{\infty\}
    \end{equation*}
    \begin{itemize}
        \item Equivalently, take $\{|1/z|<R\}$.
    \end{itemize}
    \item Let's visualize this sphere and neighborhood.
    \begin{figure}[h!]
        \centering
        \begin{tikzpicture}[
            every node/.style=black
        ]
            \footnotesize
            \fill [orz] (120:1)
                arc[start angle=-180,end angle=0,x radius=5mm,y radius=1mm]
                arc[start angle=60,end angle=120,radius=1cm]
            ;
            \draw [orx] (120:1) arc[start angle=-180,end angle=0,x radius=5mm,y radius=1mm];
    
            \draw circle (1cm);
            \draw (-1,0) arc[start angle=-180,end angle=0,x radius=1cm,y radius=2mm] node[right]{$\C$};
            \draw [dashed] (-1,0) arc[start angle=180,end angle=0,x radius=1cm,y radius=2mm];
    
            \fill [cyan] (0,1) circle (2pt) node[above right]{$\infty$};
            \fill [orx] (0,-1) circle (2pt) node[below right]{$0$};
        \end{tikzpicture}
        \caption{The Riemann sphere.}
        \label{fig:riemannSphere}
    \end{figure}
    \pagebreak
    \item \textbf{Stereographic projection}: A mapping of the sphere (minus the north pole) to the plane. Take the line from $\infty$ through a point on the sphere and onto the plane (this sets up a one-to-one correspondence between the points of the sphere and those of the plane).
    \begin{figure}[h!]
        \centering
        \begin{tikzpicture}[
            scale=1.3,
            every node/.style=black
        ]
            \footnotesize
            \draw %(-1.1,-0.3) -- 
                (-2,-0.3) -- (-3,-1.7) -- (2,-1.7) -- (3,-0.3)
                % -- (1.1,-0.3)
                -- cycle
            ;
            \draw [rex] (0,-1) ellipse (2cm and 4mm);
            \node [inner sep=1pt] at (2.2,-0.55) {$|z|=1$}
                edge [out=180,in=60,->] (1.5,-0.7)
            ;
            \draw [grx,-stealth,yshift=-1cm] (170:1.9) -- (170:-1.9) node[right]{$\R$};
            \draw [blx,-stealth,yshift=-1cm] (25:-1.5) node[above left,yshift=-1mm]{$i\R$} -- (25:1.5);
            \fill [white] circle (1.1cm);
    
            \draw [rex,name path=equator] (-1,0) arc[start angle=-180,end angle=0,x radius=1cm,y radius=2mm];
            \draw [rex,dashed] (-1,0) arc[start angle=180,end angle=0,x radius=1cm,y radius=2mm];
            \draw [grx,name path=real] (0,-1) arc[start angle=-90,end angle=90,x radius=7.7mm,y radius=1cm];
            \draw [grx,dashed] (0,-1) arc[start angle=-90,end angle=-270,x radius=7.7mm,y radius=1cm];
            \draw [blx,name path=imaginary] (0,-1) arc[start angle=-90,end angle=-270,x radius=4mm,y radius=1cm];
            \draw [blx,dashed] (0,-1) arc[start angle=-90,end angle=90,x radius=4mm,y radius=1cm];
    
            % \path (-2,-1) arc[start angle=-180,end angle=-150,x radius=2cm,y radius=4mm] coordinate (p);
            % \fill [rex] (p) circle (1pt);
            % \draw [help lines,name path=p] (p) -- (0,1);
            % \fill [rex,name intersections={of=equator and p}] (intersection-1) circle (1pt);
            \path (-2,-1) arc[start angle=-180,end angle=-80,x radius=2cm,y radius=4mm] coordinate (q);
            \fill [rex] (q) circle (1pt);
            \draw [help lines,name path=q] (q) -- (0,1);
            \fill [rex,name intersections={of=equator and q}] (intersection-1) circle (1pt);
    
            \coordinate (r) at ([yshift=-1cm]170:-1);
            \fill [grx] (r) circle (1pt);
            \draw [help lines,name path=r] (r) -- (0,1);
            \fill [grx,name intersections={of=real and r}] (intersection-1) circle (1pt);
    
            \coordinate (s) at ([yshift=-1cm]25:-1.3);
            \fill [blx] (s) circle (1pt);
            \draw [help lines,name path=s] (s) -- (0,1);
            \fill [blx,name intersections={of=imaginary and s}] (intersection-1) circle (1pt);
    
            \draw circle (1cm);
            \fill [cyan] (0,1) circle (1.5pt) node[above=1pt]{$\infty$};
            \fill [orx] (0,-1) circle (1.5pt) node[below=1pt]{$0$};
        \end{tikzpicture}
        \caption{Stereographic projection.}
        \label{fig:stereographicProjection}
    \end{figure}
    \begin{itemize}
        \item Put $\{0\}$ at the point of tangency.
        \item The equator will get mapped to a circle, so the stereographic projection is actually conformal away from $\infty$!
        \begin{itemize}
            \item Moreover, we will identify this circle with the unit circle.
        \end{itemize}
        \item The real axis will become a line of longitude/great circle.
        \item The imaginary axis will become the complementary line of longitude.
        \item So the real and imaginary axes, and the unit circle become three perpendicular great circles on the Riemann sphere.
    \end{itemize}
    \item This allows us to give an alternate definition of being meromorphic: $f$ on $U\subset\C$ is meromorphic if $f:U\to\hat{\C}$ is such that $f^{-1}(\infty)$ is discrete and $f|_{U\setminus f^{-1}(\infty)}$ is holomorphic.
    \item As a complex manifold: Let $f:U\ni\infty\to\C$ be a function. We say that $f$ is holomorphic at $\infty$ if
    \begin{equation*}
        f^*(z) :=
        \begin{cases}
            f(1/z) & z\neq 0\\
            f(\infty) & z=0
        \end{cases}
    \end{equation*}
    is holomorphic at zero.
    \item Exercise: In Figure \ref{fig:stereographicProjection}, we projected the Riemann sphere down onto a plane tangent to the sphere at 0. What if we project the Riemann sphere up onto a plane tangent to the sphere at $\infty$? Clearly these two versions of the complex plane would be parallel, and it actually turns out that the map between them is just $z\mapsto 1/z$!
    \item TPS: Verify that $1/(z-3)^2$ is holomorphic at $\infty$.
    \begin{itemize}
        \item Note: This is a pole of order 2 at $z=3$.
        \item We have that
        \begin{equation*}
            f^*(z) =
            \begin{cases}
                \frac{z^2}{(1-3z)^2} & z\neq 0\\
                0 & z=0
            \end{cases}
        \end{equation*}
        \item Clearly, $\lim_{z\to 0}f^*(z)=0$, so we're done.
        \item Comments.
        \begin{itemize}
            \item Saying something \emph{is} holomorphic at $\infty$ is just saying that it has an analytic continuation at $\infty$ (via Riemann's removable singularity theorem).
            \item $f^*$ has a zero of order 2 at $\infty$.
        \end{itemize}
    \end{itemize}
    \item In order to work with the Riemann sphere, you always put a patch of it on the plane and then say, "well, we know complex analysis on the plane."
    \begin{itemize}
        \item Thus, we have a notion of poles, zeroes, and holomorphisms at $\infty$.
    \end{itemize}
    \item The open mapping theorem still applies!
    \begin{itemize}
        \item If $U$ is a domain and $f:U\subset\hat{C}\to\C$ is holomorphic, then $f(U)$ is open.
    \end{itemize}
    \item More generally, we should do something about the Riemann sphere.
    \item \textbf{Riemann surface}: A (real) two-manifold (locally like $\R^2$) equipped with an atlas of \textbf{charts}. \emph{Denoted by} $\bm{X}$.
    \item \textbf{Chart}: A map from a domain $U$ on the Riemann surface in question down to the complex plane $\C$ that is locally biholomorphic. \emph{Denoted by} $\bm{\phi_U}$.
    \item \textbf{Holomorphic} ($f$ at $z\in X$): A function $f:U\to\C$ for which $f\circ\phi_U^{-1}$ is holomorphic at $\phi_U(z)$, where $X$ is a Riemann surface and $z\in U\subset X$.
    \item Suppose we map the bottom \emph{and} top halves of the Riemann sphere to the unit circle.
    \begin{itemize}
        \item The interconversion map is once again $1/z$.
    \end{itemize}
    \item We're now done \emph{defining} the Riemann sphere. We now start doing \emph{analysis} on the Riemann sphere.
    \item Observation: $f$ is holomorphic at $\infty$ iff $f(1/z)$ is holomorphic at 0.
    \begin{itemize}
        \item Thus, $f:U\supset\hat{\C}\to\hat{\C}$ is meromorphic iff $f$ is a holomorphic map.
    \end{itemize}
    \item Theorem: Any holomorphic function $f:X\to\C$ on $\hat{\C}$ (or any compact Riemann surface $X$) is constant.
    \begin{proof}
        Since $f$ is holomorphic on $X$, $f$ is continuous on $X$. Thus, since continuous functions on compact spaces must take maximums, $|f|$ has to take a maximum on $X$. Suppose $z\in X$ is such that $|f(z)|$ is max. Take a neighborhood $U\ni z$ and its chart $\phi_U:U\to\C$. Then $\phi_U(z)$ is in the interior of $\phi_U(U)$. It follows that $f\circ\phi_U^{-1}$ is holomorphic on $\phi_U(U)\subset\subset\C$. Thus, by the maximum modulus principle, $f\circ\phi_U^{-1}$ is constant on $\phi_U(U)$. Thus, $f$ is constant on $U$. Now take overlapping coverings of $U$ to expand the constancy over all of $X$, i.e., invoke the identity theorem.
    \end{proof}
    \item Note: This method of proof (doing something on a chart and then expanding over) is common.
    \item Corollary (Liouville's theorem): If $f\in\mO(\C)$ and bounded, then $f$ is constant.
    \begin{proof}
        If it's bounded on $\C$, then it's bounded in a neighborhood of $\infty$. Thus, we do the inversion to $f^*$ which has an analytic continuation to 0, so $f$ is holomorphic on $\hat{\C}$ and hence, by the previous theorem, $f$ is constant.
    \end{proof}
    \item Implication: Holomorphic functions on the Riemann sphere are constant (hence relatively uninteresting).
    \item More interesting: Let's look at meromorphic functions on $\hat{\C}$.
    \begin{itemize}
        \item Examples: $1/z$, $z$, $z^2$, polynomials, rational functions.
        \begin{itemize}
            \item This is it!
        \end{itemize}
        \item Nonexample: The exponential map is \emph{not} meromorphic on $\hat{\C}$ because it actually has an essential singularity at $\infty$: $R\to\infty$ goes to $\infty$, but $R\to-\infty$ goes to 0.
    \end{itemize}
    \item Claim: Any meromorphic function on the Riemann sphere is a rational function.
    \begin{proof}
        Done next Tuesday.
    \end{proof}
    \item There are lots of meromorphic functions that are called rational functions on other compact Riemann surfaces.
    \item Example: $zy^2=x^3+axz^2+bz^3$ gives a set of points in $\C^2$ or $\R^2$.
    \begin{itemize}
        \item Actually defines a genus 1 surface?? Could work for a final project!
        \item The function $[x:y:z]\mapsto x/z$ is meromorphic. This map looks like skewering the torus and rotating it like a kebob.
        \item What is going on here??
    \end{itemize}
    \item Proposition: Let $f:X\to\hat{\C}$ be meromorphic and nonconstant, where $X$ is a compact Riemann surface. Then $f$ is onto.
    \begin{proof}
        We want to show that $f(X)=\hat{\C}$. By the open mapping theorem, $f(X)$ is open. But $X$ is compact, which means that $f(X)$ is compact, which means that $f(X)$ is closed. Thus, $\hat{\C}\setminus f(X)$ is open. But then $f(X)$ and $\hat{\C}\setminus f(X)$ partition $\hat{\C}$ into disjoint open subsets, so since $\hat{\C}$ is connected, one of these sets must be empty. $f(X)$ is nonempty, so $\hat{\C}\setminus f(X)$ must be empty and therefore $f(X)=\hat{\C}$, as desired.
    \end{proof}
    \item Corollary: Fundamental Theorem of Algebra.
    \begin{proof}
        Given a polynomial, there exists a root. How does this work??
    \end{proof}
\end{itemize}




\end{document}