\documentclass[../finalProject.tex]{subfiles}

\pagestyle{main}
\renewcommand{\leftmark}{Written Report Feedback Form}
\renewcommand{\proofname}{Response}

\begin{document}




\section*{Written Report Feedback Form}
\addcontentsline{toc}{section}{Written Report Feedback Form - Daniel}
\marginnote{5/19:}\textbf{Report writer}: Daniel Luna\\
\textbf{Person giving feedback}: Steven Labalme\\
\medskip

\noindent Instructions: Everyone must get feedback on their report from one person and must give feedback to at least one other person. In addition to completing this form, you are expected to read through the report and make constructive comments. The writer should upload this completed form as well as a copy of the draft with any feedback recorded on it.\\
\bigskip

\noindent In one sentence, what was this project about? What was the main result?
\begin{proof}
    Daniel motivated, stated, proved, and discussed the consequences of Picard's big theorem.
\end{proof}
\vspace{3em}

\noindent What did you find most interesting about this subject?
\begin{proof}
    I thought it was a neat tie-together of several important and mentally challenging class concepts. Daniel also supplemented these with more details about the proofs than were presented, and gave examples of extensions.
\end{proof}
\vspace{3em}

\noindent Were there any places in the report that you were confused?
\begin{proof}
    Not really --- it was well-explained! Make sure you define that alternate notation for the winding number, though, in your discussion of Cauchy's residue theorem. We've seen $\wn(\Gamma,z)$ in class, so \textcite{bib:FischerLieb}'s $n(\Gamma,z)$ should be explained.\par
    One other more general comment would be to include a few more examples of things you allude to. For instance, you say several times that Picard's big theorem and essential singularities have applications outside of pure math research but never mention any of these. An example or two would be cool!
\end{proof}
\vspace{3em}

\noindent Were there any pictures, examples, or analogies that you found especially enlightening?
\begin{proof}
    The whole paper was beautifully and lyrically written from start to finish. Fixed point theorems have something of a special place in my heart, so it was cool to see that tie-in!
\end{proof}
\vspace{3em}

\noindent Write a bullet-point outline of the report.
\begin{proof}
    {\color{white}Easter egg!!}
    \begin{itemize}
        \item Significance of Picard's big theorem draws in the reader.
        \item Historical background situates Picard's big theorem in its context.
        \item Mathematical prerequisites from class.
        \item Proof of the main result.
        \item Mathematical consequences of the main result.
    \end{itemize}
\end{proof}




\end{document}